Measurement and Probability in Fuzzy Quantum Theories

### 2017-06-06 prop_iop.tex
prop_iop.tex \subsection{From Real-valued to Interval-valued} Updating..

\begin{definition}We say a pair~$\left(\mathscr{I},\iota\right)$
is regular\footnote{\yutsung{''regular'' is just a random name pop into my mind...

This whole definition might be rewritten using category theory...
I would investigate it if it is necessary...}} if $\mathscr{I}$ is a collection of intervals and $\iota:\left[0,1\right]\rightarrow\mathscr{I}$
is a function satisfying the following properties. 
\begin{itemize}
\item $\iota\left(0\right)=\left[0,0\right]$. 
\item $\iota\left(1\right)=\left[1,1\right]$. 
\item For any $x\in\left[0,1\right]$, $\iota\left(1-x\right)=\left[1,1\right]-\iota\left(x\right)$. 
\item For a set $\left\{ x_{i}\right\} _{i=1}^{N}\subseteq\left[0,1\right]$,
if $\sum_{i=1}^{N}x_{i}\in\left[0,1\right]$, then $\iota\left(\sum_{i=1}^{N}x_{i}\right)\subseteq\sum_{i=1}^{N}\iota\left(x_{i}\right)$. 
\end{itemize}
\end{definition}

\begin{lemma}\label{lemma:real2interval}Consider a regular pair~$\left(\mathscr{I},\iota\right)$.
Then, given a quantum probability measure~$\mu:\events\rightarrow\left[0,1\right]$,
a function~$\bar{\mu}:\events\rightarrow\mathscr{I}$ defined by
$\bar{\mu}(P)=\iota\left(\mu(P)\right)$ is a quantum IVPM.\end{lemma}

\begin{proof}~
\begin{itemize}
\item $\bar{\mu}(\mathbb{0})=\iota\left(\mu(\mathbb{0})\right)=\iota\left(0\right)=\left[0,0\right]$.
\item $\bar{\mu}(\mathbb{1})=\iota\left(\mu(\mathbb{1})\right)=\iota\left(1\right)=\left[1,1\right]$.
\item For any projection $P$, $\bar{\mu}\left(\mathbb{1}-P\right)=\iota\left(\mu(\mathbb{1}-P)\right)=\iota\left(1-\mu(P)\right)=\left[1,1\right]-\iota\left(\mu(P)\right)=\left[1,1\right]-\bar{\mu}\left(P\right)$.
\item For a set of mutually orthogonal projections $\left\{ P_{i}\right\} _{i=1}^{N}$,
we have $\sum_{i=1}^{N}\mu\left(P_{i}\right)=\mu\left(\sum_{i=1}^{N}P_{i}\right)\in\left[0,1\right]$
so that $\bar{\mu}\left(\sum_{i=1}^{N}P_{i}\right)=\iota\left(\mu\left(\sum_{i=1}^{N}P_{i}\right)\right)=\iota\left(\sum_{i=1}^{N}\mu\left(P_{i}\right)\right)\subseteq\sum_{i=1}^{N}\iota\left(\mu\left(P_{i}\right)\right)=\sum_{i=1}^{N}\bar{\mu}\left(P_{i}\right)$.
\end{itemize}
\end{proof}

\begin{lemma}Consider a regular pair~$\left(\mathscr{I},\iota\right)$.
Then, there is a quantum IVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$
such that $\mathrm{core}\left(\bar{\mu}\right)$ has an unique element.\end{lemma}

@@

\begin{example}\label{ex:regular-pair}For any positive integer~$n$,
there is a regular pair~$\left(\mathscr{I}_{n},\iota_{n}\right)$
defined by 
\begin{equation}\eqalign{ 
\mathscr{I}_{n} = \set{\left[\frac{k}{n},\frac{k}{n}\right]}{k=0,\ldots,n}\cup\set{\left[\frac{k}{n},\frac{k+1}{n}\right]}{k=0,\ldots,n-1}\\ 
\iota_{n}\left(x\right) = \cases{ 
\left[\frac{k}{n},\frac{k}{n}\right] & , if $x=\frac{k}{n}$ ;\\ 
\left[\frac{k}{n},\frac{k+1}{n}\right] & , if $\frac{k}{n}<x<\frac{k+1}{n}$ . 
} 
}\end{equation}
Notice that the usual $\left\{ \necess,\imposs,\unknown\right\} $
is $\mathscr{I}_{1}$. Also, let $\mathscr{I}_{\infty}=\set{\left\{ x\right\} }{x\in\left[0,1\right]}$
and $\iota_{\infty}\left(x\right)=\left\{ x\right\} $. Of course,
$\left(\mathscr{I}_{\infty},\iota_{\infty}\right)$ is a regular pair.\end{example}

>>>>

\begin{definition}We say a pair\nb$\left(\mathscr{I},\iota\right)$
is additive\footnote{\yutsung{This whole definition might be rewritten using category
theory... I would investigate it if it is necessary...}} if $\mathscr{I}$ is a collection of intervals and $\iota:\left[0,1\right]\rightarrow\mathscr{I}$
is a function satisfying the following properties. 
\begin{itemize}
\item $\iota\left(0\right)=\left[0,0\right]$. 
\item $\iota\left(1\right)=\left[1,1\right]$. 
\item For any $x\in\left[0,1\right]$, $\iota\left(1-x\right)=\left[1,1\right]-\iota\left(x\right)$. 
\item For a set\nb$\left\{ x_{i}\right\} _{i=1}^{N}\subseteq\left[0,1\right]$,
if $\sum_{i=1}^{N}x_{i}\in\left[0,1\right]$, then $\iota\left(\sum_{i=1}^{N}x_{i}\right)\subseteq\sum_{i=1}^{N}\iota\left(x_{i}\right)$. 
\end{itemize}
Moreover, $\left(\mathscr{I},\iota\right)$ is called convex if for
any three numbers\nb$x_{0}$, $x_{1}$, and $x_{2}\in\left[0,1\right]$,
if $x_{0}+x_{1}+x_{2}\in\left[0,1\right]$, then $\iota\left(x_{0}+x_{1}+x_{2}\right)+\iota\left(x_{2}\right)\subseteq\iota\left(x_{0}+x_{2}\right)+\iota\left(x_{1}+x_{2}\right)$.\end{definition}

\begin{lemma}\label{lemma:real2interval}Consider an additive pair\nb$\left(\mathscr{I},\iota\right)$.
Then, given a quantum probability measure\nb$\mu:\events\rightarrow\left[0,1\right]$,
a function\nb$\bar{\mu}:\events\rightarrow\mathscr{I}$ defined by
$\bar{\mu}(P)=\iota\left(\mu(P)\right)$ is a quantum IVPM. Moreover,
if $\left(\mathscr{I},\iota\right)$ is convex, then $\bar{\mu}(P)$
is a convex.\end{lemma}

\begin{proof}~
\begin{itemize}
\item $\bar{\mu}(\mathbb{0})=\iota\left(\mu(\mathbb{0})\right)=\iota\left(0\right)=\left[0,0\right]$.
\item $\bar{\mu}(\mathbb{1})=\iota\left(\mu(\mathbb{1})\right)=\iota\left(1\right)=\left[1,1\right]$.
\item For any projection $P$, $\bar{\mu}\left(\mathbb{1}-P\right)=\iota\left(\mu(\mathbb{1}-P)\right)=\iota\left(1-\mu(P)\right)=\left[1,1\right]-\iota\left(\mu(P)\right)=\left[1,1\right]-\bar{\mu}\left(P\right)$.
\item For a set of mutually orthogonal projections\nb$\left\{ P_{i}\right\} _{i=1}^{N}$,
we have $\sum_{i=1}^{N}\mu\left(P_{i}\right)=\mu\left(\sum_{i=1}^{N}P_{i}\right)\in\left[0,1\right]$
so that $\bar{\mu}\left(\sum_{i=1}^{N}P_{i}\right)=\iota\left(\mu\left(\sum_{i=1}^{N}P_{i}\right)\right)=\iota\left(\sum_{i=1}^{N}\mu\left(P_{i}\right)\right)\subseteq\sum_{i=1}^{N}\iota\left(\mu\left(P_{i}\right)\right)=\sum_{i=1}^{N}\bar{\mu}\left(P_{i}\right)$.
\item For convexity part, given a pair of commuting operators\nb$P_{0}$
and $P_{1}$, they and $P_{0}\vee P_{1}$ can be expressed by the
summation among $P_{0}\left(\mathbb{1}-P_{1}\right)$, $\left(\mathbb{1}-P_{0}\right)P_{1}$,
and $P_{0}P_{1}$. Hence, 
\begin{equation}\eqalign{ 
 & \bar{\mu}\left(P_{0}\vee P_{1}\right)+\bar{\mu}\left(P_{0}P_{1}\right)=\iota\left(\mu\left(P_{0}\vee P_{1}\right)\right)+\iota\left(\mu\left(P_{0}P_{1}\right)\right)\\
= & \iota\left(\mu\left(P_{0}\left(\mathbb{1}-P_{1}\right)\right)+\mu\left(\left(\mathbb{1}-P_{0}\right)P_{1}\right)+\mu\left(P_{0}P_{1}\right)\right)+\iota\left(\mu\left(P_{0}P_{1}\right)\right)\\
\subseteq&\iota\left(\mu\left(P_{0}\left(\mathbb{1}-P_{1}\right)\right)+\mu\left(P_{0}P_{1}\right)\right)+\iota\left(\mu\left(\left(\mathbb{1}-P_{0}\right)P_{1}\right)+\mu\left(P_{0}P_{1}\right)\right)\\
= & \iota\left(\mu\left(P_{0}\right)\right)+\iota\left(\mu\left(P_{1}\right)\right)=\bar{\mu}\left(P_{0}\right)+\bar{\mu}\left(P_{1}\right) 
}\end{equation}
\end{itemize}
\end{proof}

\begin{lemma}Consider an additive pair\nb$\left(\mathscr{I},\iota\right)$.
Then, there is a quantum IVPM\nb$\bar{\mu}:\events\rightarrow\mathscr{I}$
such that $\mathrm{core}\left(\bar{\mu}\right)$ has an unique element.
Obviously, if $\left(\mathscr{I},\iota\right)$ is convex, so does
$\bar{\mu}$.\end{lemma}

@@

\begin{example}\label{ex:regular-pair}For any positive integer~$n$,
there is an additive pair\nb$\left(\mathscr{I}_{n},\iota_{n}\right)$
defined by 
\begin{equation}\eqalign{ 
\mathscr{I}_{n} = \set{\left[\frac{k}{n},\frac{k}{n}\right]}{k=0,\ldots,n}\cup\set{\left[\frac{k}{n},\frac{k+1}{n}\right]}{k=0,\ldots,n-1}\\ 
\iota_{n}\left(x\right) = \cases{ 
\left[\frac{k}{n},\frac{k}{n}\right] & , if $x=\frac{k}{n}$ ;\\ 
\left[\frac{k}{n},\frac{k+1}{n}\right] & , if $\frac{k}{n}<x<\frac{k+1}{n}$ . 
} 
}\end{equation}
Notice that the usual $\left\{ \necess,\imposs,\unknown\right\} $
is $\mathscr{I}_{1}$. Also, let $\mathscr{I}_{\infty}=\set{\left\{ x\right\} }{x\in\left[0,1\right]}$
and $\iota_{\infty}\left(x\right)=\left\{ x\right\} $. Of course,
$\left(\mathscr{I}_{\infty},\iota_{\infty}\right)$ is a regular pair.\end{example}
